Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-20 article/article.tex
(+) Nice conclusion

\subsection{Further work}
Since all the tests has been run using Paris West area, the influence of the
complexity of the airspace has not been assessed. It would be thus relevant to
carry further tests on bigger areas. In~\cite{ferrari2017}, the time needed to
compute the cost with A\(^*\) depends heavily on the traffic itself. Therefore
the use, in this paper, of randomly generated scenarii of traffic may not be
suitable in the context of ATM\@. One can even use a more realistic workload
model such as a neural network as mentioned in~\cite{gianazza2010forecasting}.

>>>>

\section{Conclusion}
The presented work provides the basis of a method able to create dynamic
airspace overture schemes. The model is built around a quantification of the
workload felt by a air trafic controller. This quantification is then used to
create a cost function to be minimised. The highly combinatorial nature of the
problem makes it prone to be solved with stochastic methods. The Monte Carlo
tree search algorithm is then introduced since it has been used in some of the
most combinatorial problem (game of Go). In this paper, the algorithm is
modified to take into account not only a result but all the path leading to this
leaf. It is also adapted to the one-player game nature of the problem.

\paragraph{Further work}
Since all the tests has been run using the same fictitious area with the same
trafic, neither the influence of the complexity of the airspace nor of the
trafic have been assessed. It would be thus relevant to carry further tests on
bigger areas with differing trafic. This can be emphasised
by~\cite{ferrari2017}, in which the time needed to compute the cost with A\(^*\)
depends heavily on the trafic itself.

More complex workload models can also be used such as neural networks
in~\cite{gianazza2010forecasting}.
